An Efficient E-field Parallel Imaging Calibration Algorithm for Next-Generation Radio Telescopes

### 2015-11-10 cal_demo/ms.tex
started the math section of cal paper
cleaned up cal tex file

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{../mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

@@

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

@@

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
instrumentation: interferometers -- techniques: image processing -- techniques: interferometric
\end{keywords}

@@

\section{Introduction}

@@

@@

% \subsection{Figures and tables}

% Figures and tables should be placed at logical positions in the text. Don't
% worry about the exact layout, which will be handled by the publishers.

% Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
% e.g. Table~\ref{tab:example_table}.

% % Example figure
% \begin{figure}
% 	% To include a figure from a file named example.*
% 	% Allowable file formats are eps or ps if compiling using latex
% 	% or pdf, png, jpg if compiling using pdflatex
% 	\includegraphics[width=\columnwidth]{example}
%     \caption{This is an example figure. Captions appear below each figure.
% 	Give enough detail for the reader to understand what they're looking at,
% 	but leave detailed discussion to the main body of the text.}
%     \label{fig:example_figure}
% \end{figure}

% % Example table
% \begin{table}
% 	\centering
% 	\caption{This is an example table. Captions appear above each table.
% 	Remember to define the quantities, symbols and units used.}
% 	\label{tab:example_table}
% 	\begin{tabular}{lccr} % four columns, alignment for each
% 		\hline
% 		A & B & C & D\\
% 		\hline
% 		1 & 2 & 3 & 4\\
% 		2 & 4 & 6 & 8\\
% 		3 & 5 & 7 & 9\\
% 		\hline
% 	\end{tabular}
% \end{table}

\section{Conclusions}
\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

@@

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
% \begin{thebibliography}{99}
% \bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
% Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
% \bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
% Others S., 2012, Journal of Interesting Stuff, 17, 198
% \end{thebibliography}

>>>>

% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{../mnras}

\usepackage{newtxtext,newtxmath}

@@

%%%%% PACKAGES %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{color}

%%%%% CUSTOM COMMANDS %%%%%

\newcommand{\s}{\hat{\mathbf{s}}} % s-hat for sine-projected direction
\newcommand{\spix}{\hat{\mathbf{s}}_{\mathrm{pix}}}
\newcommand{\Cna}{\mathcal{C}^{(n)}_a}
\newcommand{\ri}{\mathbf{r}_i}
\newcommand{\ra}{\mathbf{r}_a}
\newcommand{\rb}{\mathbf{r}_b}
\newcommand{\Nant}{N_{\mathrm{ant}}}
\newcommand{\beamr}{\widetilde{W}}
\newcommand{\beamtheta}{W}
\newcommand{\Er}[1]{\widetilde{E}_{#1}}
\newcommand{\Erest}[1]{\hat{\widetilde{E}}_{#1}}
\newcommand{\V}{\widetilde{V}}

@@

\begin{keywords}
instrumentation: interferometers -- techniques: image processing -- techniques: interferometric
\end{keywords}

@@

\section{Introduction}
The field of radio astronomy is undergoing a paradigm shift toward interferometers consisting of hundreds to thousands of small, widefield antennas. This shift is necessary to match the survey speeds required for both precision cosmology experiments, and searches for fast radio transients. Many arrays with this design are already built or under construction including \cite{XXX}.

@@

\begin{equation}
\mathcal{C}^n(a,\spix,f) \equiv \left<E_a(f) E'^*(\spix,f)\right>_t
\end{equation}
$\mathcal{C}^n(a,\spix,f) \rightarrow \Cna$

\begin{equation}
\Er{a} = g_a E^T_a
\end{equation}
\begin{align}
\hat{E}(\spix) & = \frac{1}{\Nant} \sum_i e^{2\pi i \spix \cdot \ri} \Erest{i} \\
& = \frac{1}{\Nant} \sum_i e^{2\pi i \spix \cdot \ri} \sum_b \beamr_b(\ri-\rb) \Erest{b} \\
& = \frac{1}{\Nant} \sum_i e^{2\pi i \spix \cdot \ri} \sum_b \beamr_b(\ri-\rb) h^{(n)}_b g_b\Er{b}^T
\end{align}
We can then play a trick to transform the beam.
\begin{align}
\hat{E}(\spix) & = \frac{1}{\Nant} \sum_b h^{(n)}_b g_b\Er{b}^T e^{2\pi i \spix \cdot \rb}\sum_i \beamr_b(\ri-\rb)e^{2\pi i \spix \cdot (\ri-\rb)}\\
& = \frac{1}{\Nant} \sum_b h^{(n)}_b g_b\Er{b}^T e^{2\pi i \spix \cdot \rb}\beamtheta_b(\spix)
\end{align}

Plugging in, we get,
\begin{align}
\Cna & = \left<\Er{a} \hat{E}^*(\spix)\right>_t \\ 
& = \left<g_a \Er{a}^T \frac{1}{\Nant} \sum_b h^{*(n)}_b g^*_b\Er{b}^{*T} e^{-2\pi i \spix \cdot \rb} \beamtheta^*_b(\spix)\right>_t \\
\end{align}
Pulling time independent pieces out.
\begin{align}
\Cna & = \frac{g_a}{\Nant} \sum_b h^{*(n)}_b g^*_b \beamtheta^*_b(\spix) e^{-2\pi i \spix \cdot \rb} \left<\Er{a}^T \Er{b}^{*T} \right>_t \\
& = \frac{g_a}{\Nant} \sum_b h^{*(n)}_b g^*_b \beamtheta^*_b(\spix) e^{-2\pi i \spix \cdot \rb} \V^T_{ab}
\end{align}
Solve for $g^{(n+1)}_a$.
\begin{equation}
g^{(n+1)}_a = \Cna \Nant \left[ \sum_b h^{*(n)}_b g^{*(n)}_b \beamtheta^*_b(\spix) e^{-2\pi i \spix \cdot \rb} \V^T_{ab} \right]^{-1}
\end{equation}

In the case where $h_b = 1/g_b$, this simplifies slightly.
\begin{equation}
g^{(n+1)}_a = \Cna \Nant \left[ \sum_b \beamtheta^*_b(\spix) e^{-2\pi i \spix \cdot \rb} \V^T_{ab} \right]^{-1}
\end{equation}

@@

\section{Conclusions}
\section*{Acknowledgements}
This work has been supported by the National Science Foundation through award AST-1206552.

@@
